Results

### 2018-07-16 02_analysis.Rmd
Better session info
Nicer session info
Stop using coda

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(coda)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

coef_summary_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

# newdata <- newdata_conditions %>% 
#   bind_cols(tidyMCMC(as.mcmc(posterior_fit), estimate.method = "median",
#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_i), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

@@

coef_summary_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_f), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

@@

coef_summary_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_ci), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_cif), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_c), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_i), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_f), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_ci), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_likely_cif), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

# Session info
# Summary of hypotheses

@@

@@

```{r show-session-info}
sessionInfo()
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstanarm)
library(broom)
library(ggstance)
library(patchwork)
library(pander)
library(scales)
library(janitor)
library(huxtable)
library(here)

@@

coef_summary_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(chains_fitted_c, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

# newdata <- newdata_conditions %>% 
#   bind_cols(tidyMCMC(posterior_fit, estimate.method = "median",
#                      conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(chains_fitted_i, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

@@

coef_summary_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(chains_fitted_f, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))
```

@@

coef_summary_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(chains_fitted_ci, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(chains_fitted_cif, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(chains_fitted_likely_c, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_i <- newdata_conditions_i %>% 
  bind_cols(tidyMCMC(chains_fitted_likely_i, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_f <- newdata_conditions_f %>% 
  bind_cols(tidyMCMC(chains_fitted_likely_f, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_ci <- newdata_conditions_ci %>% 
  bind_cols(tidyMCMC(chains_fitted_likely_ci, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

coef_summary_likely_cif <- newdata_conditions_cif %>% 
  bind_cols(tidyMCMC(chains_fitted_likely_cif, estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval"))

@@

# Summary of hypotheses

@@

# Original computing environment

@@

```{r show-session-info, echo=TRUE}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```
